Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-11-14 limits/ms.tex
Fixed text.

We generate four two-component mock galaxies, where the dark matter and stellar
profiles are allowed to be both steep and shallow.  The enclosed mass in all cases
is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. These
values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.

@@

The main results from modeling these different configurations are shown in
\figref{main results} and \figref{main results pixel-wise}. Each
subplot corresponds to a different mock galaxy. We show the fractional error of the mass
distribution for each of the test configurations with (red) and without stellar mass (black)
In \figref{main results}, the error is defined over radial bins of mass as
%
\begin{equation} \label{badness}
  f_R = \frac {\sum_r \left|M_p(r) - \tilde M_p(r)\right| } {\sum \tilde M_p(r)}
\end{equation}
%
where $M_p$ is the mass in a radial bin and $\tilde M_p$ is the mass from the mock galaxy.
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
%
\begin{equation} \label{badness}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
\end{equation}
%
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

>>>>

We generate four two-component mock galaxies, where the dark matter and stellar
profiles are allowed to be both steep and shallow.  
%The enclosed mass in all cases
%is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. 
The enclosed mass of the stars and dark matter are both fixed to be 
$M_{*,\mathrm{DM}} = 1.8 \times 10^{10}$\,M$_\odot$ at the stellar scale radius 
$a_* = 2$\,kpc, such that the stars and dark matter contribute equally to the total
mass at $a_*$. The dark matter scale length is fixed for all models at $a_\mathrm{DM}
= 20$\,kpc.
These
values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.

@@

The main results from modeling these different configurations are shown in
\figref{main results} and \figref{main results pixel-wise}. Each
subplot corresponds to a different mock galaxy. We show the fractional error of the mass
distribution for each of the test configurations with (red) and without stellar mass (black)
In \figref{main results}, the error is defined over radial bins of mass as
%
\begin{equation} \label{badness}
  f_R = \frac {\sum_i \left|M_p(i) - \tilde M_p(i)\right| } {\sum \tilde M_p(i)}
\end{equation}
%
where $M_p$ is the mass in a radial bin and $\tilde M_p$ is the mass from the mock galaxy.
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
%
\begin{equation} \label{badness}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
\end{equation}
%
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.
